Multi-domain, multilingual translation with latent multi-task group dropout

### 2022-01-14 2022/acl/acl_latex.tex
shorter

Recently, \citet{biao21share} proposed jointly learning how to route between shared representation and language-specific representation via a conditional language-specific routing and the parameters of the underlying Transformer. This method is closely related to the FusionAdapters of \citet{pfeiffer21adapterfusion}. Both approaches aimed to select between shared representation and task-specific representations. The proximity between tasks is not taken into account in the routing mechanism. Our method proposed a different approach to the problem of multi-task routing in the underlying network.

>>>>

\citet{biao21share} propose to learn to route between shared and language-specific representations with a conditional language-specific routing while training the parameters of the underlying Transformer. This method is related to the FusionAdapters of \citet{pfeiffer21adapterfusion}. Both approaches aim to select between shared and task-specific representations. The proximity between tasks is not taken into account in the routing mechanism. We propose a different approach to the problem of multi-task routing in the underlying network.
